### 2023-01-08 output/DiD/tables/balance_table.tex
balance table v1

\begin{tabular}{llcccccc}
\toprule
 &  & \textit{} & \multicolumn{2}{r}{\textit{Difference in Cases Won by Defendant}} \\
 &  & Cases Won by Plaintiff & Unweighted & P-Value \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.33 \\
 & For cause (transfer) & 0.00 & -0.01 & 0.02 \\
 & Foreclosure & 0.04 & 0.03 & 0.00 \\
 & Foreclosure (transfer) & 0.00 & -0.00 & 0.77 \\
 & No cause & 0.11 & -0.02 & 0.08 \\
 & No cause (transfer) & 0.01 & -0.01 & 0.08 \\
 & Non-payment of rent & 0.71 & 0.01 & 0.78 \\
 & Non-payment of rent (transfer) & 0.01 & -0.01 & 0.02 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 \\
 & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.37 \\
 & Plaintiff is an entity & 0.66 & 0.03 & 0.13 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Total property value & 6554743.50 & 184134.63 & 0.79 \\
 & Building value & 1897711.00 & 25986.91 & 0.90 \\
 & Land value & 87585.64 & 22095.39 & 0.21 \\
 & Other value & 8535625.58 & 232361.89 & 0.78 \\
 & Units & 28.73 & -24.04 & 0.00 \\
\cline{1-5}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccc}
\toprule
 &  & \textit{} & \multicolumn{2}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
 &  & Cases Won by Plaintiff & Unweighted & P-Value \\
\midrule
\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 \\
 & Foreclosure & 0.04 & 0.03 & 0.00 \\
 & No cause & 0.11 & -0.03 & 0.03 \\
 & Non-payment of rent & 0.72 & -0.01 & 0.77 \\
 & Transferred From Other Court & 0.06 & 0.00 & 0.67 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 \\
 & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.37 \\
 & Plaintiff is an entity & 0.66 & 0.03 & 0.13 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Total property value & 6554743.50 & 184134.63 & 0.79 \\
 & Building value & 1897711.00 & 25986.91 & 0.90 \\
 & Land value & 87585.64 & 22095.39 & 0.21 \\
 & Other value & 8535625.58 & 232361.89 & 0.78 \\
 & Units & 28.73 & -24.04 & 0.00 \\
\cline{1-5}
\bottomrule
\end{tabular}

### 2023-01-08 output/summary_statistics/tables/summary_statistics.tex
balance table v1

\begin{tabular}{llcccc}
\toprule
 &  & Median & Mean & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.00 & 0.12 & 0.32 & 40,727 \\
 & For cause (transfer) & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Foreclosure & 0.00 & 0.02 & 0.14 & 40,727 \\
 & Foreclosure (transfer) & 0.00 & 0.00 & 0.03 & 40,727 \\
 & No cause & 0.00 & 0.10 & 0.30 & 40,727 \\
 & No cause (transfer) & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Non-payment of rent & 1.00 & 0.73 & 0.44 & 40,727 \\
 & Non-payment of rent (transfer) & 0.00 & 0.02 & 0.13 & 40,727 \\
\cline{1-6}
\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 0.20 & 0.40 & 40,727 \\
 & Case duration & 21.00 & 57.81 & 78.29 & 39,087 \\
 & Case heard & 0.00 & 0.06 & 0.23 & 40,727 \\
 & Case involuntarily dismissed & 0.00 & 0.29 & 0.45 & 40,727 \\
 & Case mediated & 0.00 & 0.41 & 0.49 & 40,727 \\
 & Money judgment & 0.00 & 1890.34 & 5279.49 & 40,727 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.00 & 0.09 & 0.28 & 40,727 \\
 & Defendant is an entity & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Plaintiff has an attorney & 1.00 & 0.84 & 0.37 & 40,727 \\
 & Plaintiff is an entity & 1.00 & 0.70 & 0.46 & 40,727 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 192400.00 & 2471065.61 & 6218383.08 & 36,587 \\
 & Land value & 1000.00 & 112575.80 & 659661.29 & 36,587 \\
 & Other value & 954900.00 & 10900678.30 & 26482630.60 & 36,587 \\
 & Total property value & 636500.00 & 8350204.19 & 22073916.94 & 36,587 \\
 & Units & 0.00 & 40.76 & 157.57 & 36,587 \\
\cline{1-6}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 213270.60 & 261462.86 & 238040.64 & 9,842 \\
 & Four years before latest docket date & 225065.75 & 280243.32 & 276051.45 & 9,968 \\
 & Latest docket date & 305144.00 & 377384.02 & 316645.29 & 10,096 \\
 & One year after latest docket date & 347550.00 & 421601.75 & 344328.86 & 10,443 \\
 & One year before latest docket date & 278722.25 & 351172.05 & 311982.74 & 10,190 \\
 & Three years after latest docket date & 414600.00 & 501611.80 & 780467.01 & 5,894 \\
 & Three years before latest docket date & 240097.38 & 307137.16 & 369763.53 & 10,172 \\
 & Two years after latest docket date & 393900.00 & 477948.08 & 457694.83 & 9,175 \\
 & Two years before latest docket date & 259176.00 & 341084.08 & 987145.51 & 10,182 \\
\cline{1-6}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & Median & Mean & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.00 & 0.12 & 0.33 & 40,727 \\
 & Foreclosure & 0.00 & 0.02 & 0.14 & 40,727 \\
 & No cause & 0.00 & 0.11 & 0.31 & 40,727 \\
 & Non-payment of rent & 1.00 & 0.75 & 0.43 & 40,727 \\
 & Transferred from Other Court & 0.00 & 0.05 & 0.22 & 40,727 \\
\cline{1-6}
\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 0.20 & 0.40 & 40,727 \\
 & Case duration & 21.00 & 57.81 & 78.29 & 39,087 \\
 & Case heard & 0.00 & 0.06 & 0.23 & 40,727 \\
 & Case involuntarily dismissed & 0.00 & 0.29 & 0.45 & 40,727 \\
 & Case mediated & 0.00 & 0.41 & 0.49 & 40,727 \\
 & Money judgment & 0.00 & 1890.34 & 5279.49 & 40,727 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.00 & 0.09 & 0.28 & 40,727 \\
 & Defendant is an entity & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Plaintiff has an attorney & 1.00 & 0.84 & 0.37 & 40,727 \\
 & Plaintiff is an entity & 1.00 & 0.70 & 0.46 & 40,727 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 192400.00 & 2471065.61 & 6218383.08 & 36,587 \\
 & Land value & 1000.00 & 112575.80 & 659661.29 & 36,587 \\
 & Other value & 954900.00 & 10900678.30 & 26482630.60 & 36,587 \\
 & Total property value & 636500.00 & 8350204.19 & 22073916.94 & 36,587 \\
 & Units & 0.00 & 40.76 & 157.57 & 36,587 \\
\cline{1-6}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 213270.60 & 261462.86 & 238040.64 & 9,842 \\
 & Four years before latest docket date & 225065.75 & 280243.32 & 276051.45 & 9,968 \\
 & Latest docket date & 305144.00 & 377384.02 & 316645.29 & 10,096 \\
 & One year after latest docket date & 347550.00 & 421601.75 & 344328.86 & 10,443 \\
 & One year before latest docket date & 278722.25 & 351172.05 & 311982.74 & 10,190 \\
 & Three years after latest docket date & 414600.00 & 501611.80 & 780467.01 & 5,894 \\
 & Three years before latest docket date & 240097.38 & 307137.16 & 369763.53 & 10,172 \\
 & Two years after latest docket date & 393900.00 & 477948.08 & 457694.83 & 9,175 \\
 & Two years before latest docket date & 259176.00 & 341084.08 & 987145.51 & 10,182 \\
\cline{1-6}
\bottomrule
\end{tabular}
